Note on coherent state

### 2020-03-19 notes/coherent state.tex
相干态的波函数note

    \begin{itemize}
        \item Basic propertities for creation and annihilation operators.
        \item Coherent states under Hamiltonian representation.
        \item Coherent states under coordinate representation.
        \item Wigner functions for coherent states and time evolution.
        \item classical propertities of coherent states.
    \end{itemize}

@@

@@

        Recall that all $\hat{D}(\alpha)$ forms a group representation of $(\mathbb{C}, +)$, it can also be considered as a group representation of $(\mathbb{R}^2, +)$, where the $\mathbb{R}^2$ represnts the x and p coordinate, which is actually a point in the phase space. So a coherent state is actually a group action by a point in the phase space, and the evolution of a coherent state is a group action by a trajectory in the phase space.

@@

@@

        \begin{equation}
            \begin{split}    
                \hat{D}(\alpha)\ket{x} &= \exp\biggl(i\Im(\alpha)\sqrt{\frac{2m\alpha}{\hbar}}\hat{x}\biggr) \exp\biggl(-i\Re(\alpha)\sqrt{\frac{2}{m\hbar\omega}}\hat{p}\biggr) \exp(-i \Im(\alpha)\Re(\alpha)) \ket{x} \\
                    &= \exp\biggl(i\Im(\alpha)\sqrt{\frac{2m\omega}{\hbar}}\bigl(x-\Re(\alpha)\sqrt{\frac{2\hbar}{m\omega}}\bigr)\biggr) \exp(-i \Im(\alpha)\Re(\alpha)) \ket{x-\Re(\alpha)\sqrt{\frac{2\hbar}{m\omega}}} 
            \end{split}
        \end{equation}

>>>>

    \begin{itemize}
        \item Basic knowledges on oscillators and coherent states.
        \item Coherent states under Hamiltonian representation and time.
        \item Coherent states under coordinate representation.
        \item Wigner functions for coherent states and time evolution.
        \item classical propertities of coherent states.
    \end{itemize}

@@

        This formula tell us the commutation property of $\exp(\hat{A})$ and $\exp(\hat{B})$ which is called Weyl commutation relation:

        \begin{equation}
            \exp(\hat{A})\exp(\hat{B}) = \exp(\hat{B})\exp(\hat{A})\exp([\hat{A}, \hat{B}])
        \end{equation}

@@

        Recall that all $\hat{D}(\alpha)$ forms a group representation of $(\mathbb{C}, +)$, it can also be considered as a group representation of $(\mathbb{R}^2, +)$, where the $\mathbb{R}^2$ represnts the x and p coordinate, which is actually a point in the phase space. So a coherent state is actually a group action by a point $(\Im(\alpha)\sqrt{\frac{2m\omega}{\hbar}}, \Re(\alpha)\sqrt{\frac{2}{m\hbar\omega}})$ in the phase space, and the evolution of a coherent state is a group action by a trajectory in the phase space. Therefore, we may use points and trajectories to describe coherent states of an oscillator.

@@

        Now that the translation operator is a group representation of $(\mathbb{R}^2, +)$, where $\mathbb{R}^2$ is the phase space, the evolution of $\ket{\alpha(t)}$ corresponds to $(\Im(\alpha\exp(-i\omega t))\sqrt{\frac{2m\omega}{\hbar}}, \Re(\alpha\exp(-i\omega t))\sqrt{\frac{2}{m\hbar\omega}})$. So we can use a circle in $\mathbb{C}$ to described the trajectory of $\ket{\alpha(t)}$.

@@

        \begin{equation}
            \begin{split}    
                \hat{D}(-\alpha)\ket{x} &= \exp\biggl(i\Im(-\alpha)\sqrt{\frac{2m\omega}{\hbar}}\hat{x}\biggr) \exp\biggl(-i\Re(-\alpha)\sqrt{\frac{2}{m\hbar\omega}}\hat{p}\biggr) \exp(-i \Im(-\alpha)\Re(-\alpha)) \ket{x} \\
                    &= \exp\biggl(-i\Im(\alpha)\sqrt{\frac{2m\omega}{\hbar}}\bigl(x-\Re(\alpha)\sqrt{\frac{2\hbar}{m\omega}}\bigr)\biggr) \exp(-i \Im(\alpha)\Re(\alpha)) \ket{x-\Re(\alpha)\sqrt{\frac{2\hbar}{m\omega}}}  \\
                    &= \exp\biggl(-i\Im(\alpha)\sqrt{\frac{2m\omega}{\hbar}}x\biggr) \exp(i\Im(\alpha)\Re(\alpha)) \ket{x-\Re(\alpha)\sqrt{\frac{2\hbar}{m\omega}}}
            \end{split}
        \end{equation}

        Therefore the wavefunction of a coherent state $\ket{\alpha}$ is

        \begin{equation}
            \begin{split}
                \Psi_\alpha(x) &= \bra{x}\hat{D}(\alpha)\ket{0} = \braket{\hat{D}(-\alpha)x|0} \\
                    &= \exp\biggl(i\Im(\alpha)\sqrt{\frac{2m\omega}{\hbar}}x\biggr) \exp(-i\Im(\alpha)\Re(\alpha)) \braket{x-\Re(\alpha)\sqrt{\frac{2\hbar}{m\omega}} | 0} \\
                    &= \exp\biggl(i\Im(\alpha)\sqrt{\frac{2m\omega}{\hbar}}x\biggr) \exp(-i\Im(\alpha)\Re(\alpha)) \exp\biggl(\frac{m\omega}{2\hbar} \bigl(x-\Re(\alpha)\sqrt{\frac{2\hbar}{m\omega}}\bigr)^2 \biggr)
            \end{split}
        \end{equation}
